Child survival for mothers: mortality change and related measures

### 2020-04-08 ALAP2020/ALAP.Rmd

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message=F, warning=F)
library(tidyverse)
library(gridExtra)
library(quadprog)
source("QOSplit.R")

options(digits=2)

# age survivor spline
lx_fun <- function(data, age){
  splinefun(data$x, data$lx, method = "monoH.FC")(age)
}
library(wpp2019)
```

@@

$$\frac{\Delta CS_{a}}{CS_a} = - \left[\int_{0}^{a}{\mu_t  \, \frac{CS_{a-t}}{CS_a} \,dt \,}\right] \Delta \delta$$
```{r main_funtion}
# function to calculate all the measures

@@

# lt must downloaded manually
lt_paises_LA <- readxl::read_xlsx("Data/WPP2019_MORT_F17_3_ABRIDGED_LIFE_TABLE_FEMALE.xlsx", sheet = 1, range = "A17:T77381") %>% rename(country_code=5,
                                      x = "Age (x)", 
                                      mx = "Central death rate m(x,n)",
                                      qx = "Probability of dying q(x,n)",
                                      dx = "Number of deaths d(x,n)",
                                      lx = "Number of survivors l(x)",
                                      Lx_n = "Number of person-years lived L(x,n)",
                                      ex = "Expectation of life e(x)")  %>% 
  select(country_code,Period,x, mx, qx, dx, lx, Lx_n, ex) %>% 
  filter(country_code %in% paises_LA_seleccion)

@@

* The proposed meassures are applied to two different demographic regimes.

[PENDING]

* A computation approach is used to evaluate the relative contribution of each component given a relative change in $\delta$.

[PENDING]

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>",
                      message=F, warning=F)
library(tidyverse)
library(gridExtra)
library(quadprog)
library(wpp2019)
source("QOSplit.R")
options(digits=2)
```

@@

$$\frac{\Delta CS_{a}}{CS_a} = - \left[\int_{0}^{a}{\mu_t  \, \frac{CS_{a-t}}{CS_a} \,dt \,}\right] \Delta \delta$$
```{r main_funtion}
# age survivor spline

lx_fun <- function(data, age){
  splinefun(data$x, data$lx, method = "monoH.FC")(age)
}

# function to calculate all the measures

@@

# lt must downloaded manually
lt_paises_LA <- readxl::read_xlsx("WPP2019_MORT_F17_3_ABRIDGED_LIFE_TABLE_FEMALE.xlsx", sheet = 1, range = "A17:T77381") %>% rename(country_code=5,
                                      x = "Age (x)", 
                                      mx = "Central death rate m(x,n)",
                                      qx = "Probability of dying q(x,n)",
                                      dx = "Number of deaths d(x,n)",
                                      lx = "Number of survivors l(x)",
                                      Lx_n = "Number of person-years lived L(x,n)",
                                      ex = "Expectation of life e(x)")  %>% 
  select(country_code,Period,x, mx, qx, dx, lx, Lx_n, ex) %>% 
  filter(country_code %in% paises_LA_seleccion)

@@
